### 2013-09-13 mr_background.tex
fixed citations; more to be fixed

\subsection{Diffusion-weighted imaging}
DWI is based on the free movement of water particles in tissue and measures the
degree of motion restriction.13 Normal prostatic tissue is very glandular with
plenty of water molecule movement. On the other hand, tumors have high cellular
density and restricted water movement, which leads to decreased diffusion. Due
to this restricted diffusion, tumors seem to be of higher intensity on
DWI.~\cite{Koh2007}

@@

A variety of different approaches can be used to analyze DCE-MRI and no report
has, up to date, described the superiority of one method over the others.3 The
approaches include qualitative analysis by visual assessment of the images,
semi-quantitative methods that look at kinetic parameters on a voxel-by-voxel
basis, or quantitative methods that that convert signal intensity into kinetic
parameters to determine how much contrast is being exchanged between the
vascular, extravascular and extracellular spaces.~\cite{Gupta2013}

>>>>

\subsection{Diffusion-weighted imaging}
DWI is based on the free movement of water particles in tissue and measures the
degree of motion restriction.~\cite{Koh2007} Normal prostatic tissue is very glandular with
plenty of water molecule movement. On the other hand, tumors have high cellular
density and restricted water movement, which leads to decreased diffusion. Due
to this restricted diffusion, tumors seem to be of higher intensity on
DWI.~\cite{Koh2007}

@@

A variety of different approaches can be used to analyze DCE-MRI and no report
has, up to date, described the superiority of one method over the others.~\cite{Gupta2013} The
approaches include qualitative analysis by visual assessment of the images,
semi-quantitative methods that look at kinetic parameters on a voxel-by-voxel
basis, or quantitative methods that that convert signal intensity into kinetic
parameters to determine how much contrast is being exchanged between the
vascular, extravascular and extracellular spaces.~\cite{Gupta2013}
